Security Metrics for the Android Ecosystem

### 2015-07-27 spsm04-thomas.tex
Add update bottleneck as a contribution
Use month rather than date information in ecosystem figure

In summary, the contributions of this paper are:
\begin{itemize}
 \item We quantify the Android update process, providing concrete numbers on the flow of updates and their latency~(\S\ref{sec:android_ecosystem}).
 \item We propose the FUM scoring metric to evaluate the security of different instances of a platform~(\S\ref{sec:security_scoring:method}).
 \item We measure the security of Android against our scoring metric and compare different device manufacturers, device models and network operators to allow device purchasers to differentiate between them based on security~(\S\ref{sec:security_scoring:results}).
\end{itemize}

@@

\label{sec:android_update_process}
\begin{figure}[h]
 \centering
 \def\svgwidth{\columnwidth}
 \import{figures/}{update_ecosystem.pdf_tex}
 \caption{Flow of updates between participants in the Android ecosystem.
 Numbers on edges indicate updates shipped between \daStartDate\ and \daEndDate, those in brackets represent number of such entities.
 Dotted arrows indicate flows where we can't measure because no public data is available.}
 \label{fig:update_ecosystem}
\end{figure}
\begin{table}
\centering
\normalsize
\begin{tabular}{l|r|r}
Project	&	\# releases	&	latency (days) \\ \hline
linux	&	\linuxNumVersions	&	\linuxMeanUpdateLatency \\
openssl	&	\opensslNumVersions	&	\opensslMeanUpdateLatency \\
bouncycastle	&	\bouncycastleNumVersions	&	\bouncycastleMeanUpdateLatency \\
\end{tabular}
\caption{Flow of updates from upstream projects into Android. Number of updates as in Figure~\ref{fig:update_ecosystem}, latency in days between the upstream release and the release of the first Android version containing it, for all pairs of versions we have data on.\todolater{scrape the other 26 websites... is it worth it?}}
\label{tab:update_ecosystem}
\end{table}
To understand how vulnerabilities in Android are fixed we examine the Android update process, which we model in Figure~\ref{fig:update_ecosystem}.
There are five entities or groups that contribute towards Android updates: the network operators, the device manufacturers, the hardware developers, Google and the upstream open source projects.
Android builds on various open source projects, such as the Linux kernel, OpenSSL and BouncyCastle cryptography libraries.
Consequently Android can include any compatible versions of those projects, including those that fix security vulnerabilities.
Android also incorporates various drivers for different bits of hardware.
The Android platform is then built from these components by Google.
The code for each Android release or update is kept secret until after a binary release has been published.\footnote{\url{https://source.android.com/source/code-lines.html}}
Device manufacturers receive advanced access in order to prepare handsets.
The network operator may then make or request customisations and perform testing before shipping the update to the device.
Sometimes device manufactures ship updates directly to the user without involving the network operator.
Sometimes the device manufacturer and Google collaborate closely to make a particular phone, such as with Nexus devices and so Google ships directly to the device.
Sometimes device manufacturers incorporate upstream open source project releases directly, and sometimes incorrectly -- for example previous work has recorded evidence of broken nightly builds of sqlite in Android releases on some device models~\cite{Wagner2013}.

>>>>

In summary, the contributions of this paper are:
\begin{itemize}
 \item We quantify the Android update process, providing concrete numbers on the flow of updates and their latency~(\S\ref{sec:android_ecosystem}).
 \item We determine that the main update bottleneck lies with manufacturers rather than operators or users~(\S\ref{sec:bottleneck}).
 \item We propose the FUM scoring metric to evaluate the security of different instances of a platform~(\S\ref{sec:security_scoring:method}).
 \item We measure the security of Android against our scoring metric and compare different device manufacturers, device models and network operators to allow device purchasers to differentiate between them based on security~(\S\ref{sec:security_scoring:results}).
\end{itemize}

@@

\label{sec:android_update_process}
\begin{figure}[h]
 \centering
 \def\svgwidth{\columnwidth}
 \import{figures/}{update_ecosystem.pdf_tex}
 \caption{Flow of updates between participants in the Android ecosystem.
 Numbers on edges indicate updates shipped between \daStartDateMonth\ and \daEndDateMonth, those in brackets represent number of such entities.
 Dotted arrows indicate flows where we can't measure because no public data is available.}
 \label{fig:update_ecosystem}
\end{figure}
\begin{table}
\centering
\normalsize
\begin{tabular}{l|r|r}
Project	&	\# releases	&	latency (days) \\ \hline
linux	&	\linuxNumVersions	&	\linuxMeanUpdateLatency \\
openssl	&	\opensslNumVersions	&	\opensslMeanUpdateLatency \\
bouncycastle	&	\bouncycastleNumVersions	&	\bouncycastleMeanUpdateLatency \\
\end{tabular}
\caption{Flow of updates from upstream projects into Android. Number of updates as in Figure~\ref{fig:update_ecosystem}, latency in days between the upstream release and the release of the first Android version containing it, for all pairs of versions we have data on.\todolater{scrape the other 26 websites... is it worth it?}}
\label{tab:update_ecosystem}
\end{table}
To understand how vulnerabilities in Android are fixed we examine the Android update process, which we model in Figure~\ref{fig:update_ecosystem}.
There are five entities or groups that contribute towards Android updates: the network operators, the device manufacturers, the hardware developers, Google and the upstream open source projects.
Android builds on various open source projects, such as the Linux kernel, OpenSSL and BouncyCastle cryptography libraries.
Consequently Android can include any compatible versions of those projects, including those that fix security vulnerabilities.
Android also incorporates various drivers for different bits of hardware.
The Android platform is then built from these components by Google.
The code for each Android release or update is kept secret until after a binary release has been published.\footnote{\url{https://source.android.com/source/code-lines.html}}
Device manufacturers receive advanced access in order to prepare handsets.
The network operator may then make or request customisations and perform testing before shipping the update to the device.
Sometimes device manufactures ship updates directly to the user without involving the network operator.
Sometimes the device manufacturer and Google collaborate closely to make a particular phone, such as with Nexus devices and so Google ships directly to the device.
Sometimes device manufacturers incorporate upstream open source project releases directly, and sometimes incorrectly -- for example previous work has recorded evidence of broken nightly builds of sqlite in Android releases on some device models~\cite{Wagner2013}.
